Thermodynamic fragments in magic state theories

### 2020-09-29 magic_paper.tex
Plot of bounds

We further define the two balanced combinations of $\Phi_\ell, \Phi_\ell^{\rm{alt}}$ for all $m\in [0,n]$,
\begin{align}	
	\Phi_+(m; n, p) &\coloneqq \frac{1}{2} \left( \Phi_\ell(m; n, p) + \Phi_\ell^{\rm{alt}}(m; n, p) \right), \\
	\Phi_-(m; n, p) &\coloneqq \frac{1}{2} \left( \Phi_\ell(m; n, p) - \Phi_\ell^{\rm{alt}}(m; n, p) \right), \\
	\Phi(m; n, p) &\coloneqq \label{eq:phi}
	\begin{cases}
		\Phi_+(m; n, p),\ \text{for even }m\in[0,n] \\
		\Phi_-(m; n, p),\ \text{for odd }m\in[0,n].
	\end{cases}
\end{align}
\begin{lemma}\label{lem:phi_bounds}
	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
		&\text{2. } \Phi(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
		&\text{3. } \Phi(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
		&\hspace{14pt} m\in [0,n-2]
		\end{split}
		\\
		&\text{4. } \nick{!!!}
	\end{align*}
\end{lemma}
\begin{proof}
	Bound 1 follows directly from~\cref{lem:comb_bounds}.

	Bounds 2,3 follow from bounds 2,3 in~\cref{lem:phil_bounds} combined with~\cref{eq:phi,eq:alt_bound}.
\end{proof}

>>>>

We further define the two balanced combinations of $\Phi_\ell, \Phi_\ell^{\rm{alt}}$ for all $m\in [0,n]$,
\begin{align}	
	\Phi_+(m; n, p) &\coloneqq \frac{1}{2} \left( \Phi_\ell(m; n, p) + \Phi_\ell^{\rm{alt}}(m; n, p) \right), \\
	\Phi_-(m; n, p) &\coloneqq \frac{1}{2} \left( \Phi_\ell(m; n, p) - \Phi_\ell^{\rm{alt}}(m; n, p) \right), \\
	\Phi(m; n, p) &\coloneqq \label{eq:phi}
	\begin{cases}
		\Phi_+(m; n, p),\ \text{for even }m\in[0,n] \\
		\Phi_-(m; n, p),\ \text{for odd }m\in[0,n].
	\end{cases}
\end{align}
\begin{lemma}\label{lem:phi_bounds}
	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
		&\text{2. } \Phi(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
		&\text{3. } \Phi(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
		&\hspace{14pt} m\in [0,n-2]
		\end{split}
	\end{align*}
\end{lemma}
\begin{proof}
	Bound 1 follows directly from~\cref{lem:comb_bounds}.

	Bounds 2,3 follow from bounds 2,3 in~\cref{lem:phil_bounds} combined with~\cref{eq:phi,eq:alt_bound}.
\end{proof}
\begin{lemma}\label{lem:phi_strictbounds}
	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_+(2m; n, p) \geq \sum_{0\leq j \leq m}\left[ 8(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
		&\hspace{14pt} m\in [1,\left\lceil\frac{n}{2}\right\rceil] \\
		&\text{2. } \Phi_+(2m; n, p) \leq \sum_{0\leq j \leq m}\left[ 2\pi(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
		&\hspace{14pt} m\in [1,\left\lceil\frac{n}{2}\right\rceil] \\
		&\text{3. } \Phi_-(2m+1; n, p) \geq \sum_{0\leq j \leq m}\left[ 8(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
		&\hspace{14pt} m\in [1,\left\lceil\frac{n-1}{2}\right\rceil] \\
		&\text{4. } \Phi_-(2m+1; n, p) \leq \sum_{0\leq j \leq m}\left[ 2\pi(2j)\left(1-\frac{2j}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2j}{n}}{p}}, \\
		&\hspace{14pt} m\in [1,\left\lceil\frac{n-1}{2}\right\rceil] \\
		\end{split}
	\end{align*}
\end{lemma}
\begin{proof}
	The bounds are direct consequences of~\cref{lem:comb_bounds}.
\end{proof}

\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/phi_bounds.pdf}
    \caption{\textbf{Cumulative binomial distribution bounds}
    Distributions $\Phi_\ell, \Phi_+$ are plotted for $n=100$ and $p=1/9$.
    The first three bounds are given in~\cref{lem:phil_bounds,lem:phi_bounds} and are valid for both $\Phi_\ell$ and $\Phi_+$.
    The fourth bound is given in~\cref{lem:phil_bounds} and is only valid for $\Phi_\ell$.
    The fifth and sixth bounds are quite strict and given in~\cref{lem:phi_strictbounds} for $\Phi_+$.
    }
    \label{fig:lccalc}
\end{figure}
